Instructions for developing new pages for the MarineOmics webpage

### 2023-02-08 submissions_instructions.Rmd
Push Sam's edits to submission instruction .Rmd

---
title: "Instructions for developing new pages for the MarineOmics webpage"
bibliography: RCN_site-Nov05.bib
---

@@

This is a guide for creating a new page for the website. Of course, the website managers will work with anyone who develops new content to help develop and publish your page, but this can be used as a resource as you develop your content. In this guide are general instructions as well as examples of how to build specific features. If there is anything else you would like to see on this guide please contact Jason Johns (jasonjohns[at]ucsb.edu). Of course, do not hesitate to reach out with any other questions or comments as well.

\* Even if you comfortable with publishing websites in Github/RMarkdown, please contact Jason Johns (jasonjohns[at]ucsb.edu) before publishing any new pages so we can ensure smooth incorporation into the website.

This website is published through Github Pages directly from the [MarineOmics github repository](https://github.com/MarineOmics/marineomics.github.io). In short, each page of the website is rendered as an .html from an RMarkdown (.Rmd) document. The two most important files for publishing the general website are the .site_yml ("the yaml file") and the index.Rmd/index.html.

**.site_yml**: the 'under the hood' backbone of the website, where things like the visual appearance of the website and the navigation bar are built

@@

### **code chunks**
Below is a basic code chunk which can be inserted by clicking the green +C button on the RStudio toolbar or typing the keyboard shortcut: <br>

@@

@@

@@

You can add Bibtex references to the file RCN_site-Nov05.bib, and then refer to them in your RMarkdown by adding bibliography: RCN_site-Nov05.bib to the header and citing them in the RMarkdown document. Check out existing pages for examples.

>>>>

---
title: "Instructions for developing new pages for the MarineOmics webpage"
bibliography: "RCN_site-Nov05.bib"
---

@@

This is a guide for creating a new page for MarineOmics.github.io. Of course, the website managers will work with anyone who develops new content to help develop and publish your page, but this can be used as a resource as you develop your content. In this guide are general instructions as well as examples of how to build specific features. If there is anything else you would like to see on this guide please contact Jason Johns (jasonjohns[at]ucsb.edu). Of course, do not hesitate to reach out with any other questions or comments as well. Please also reach out to him before publishing any new pages.

This website is published through Github Pages directly from the [MarineOmics github repository](https://github.com/MarineOmics/marineomics.github.io). In short, each page of the website is rendered as an .html from an RMarkdown (.Rmd) document. The two most important files for publishing the general website are the _site.yml and the index.Rmd/index.html.

**_site.yml**: the 'under the hood' backbone of the website, where things like the visual appearance of the website and the navigation bar are built

@@

### **code chunks**
Below is a basic R code chunk which can be inserted by clicking the green +C button on the RStudio toolbar or typing the keyboard shortcut: <br>

@@

#Here's a simple linear model in R as an example
my_lm <- lm(y ~ x, data = df)

@@

# Here's a simple line of bash as an example
mkdir ~/Path/To/My/NewDir

@@

You can add Bibtex references to the file RCN_site-Nov05.bib, and then refer to them in your RMarkdown by adding bibliography: RCN_site-Nov05.bib to the header and citing them in the RMarkdown document. Let's say you have a paper you want to cite by LastName et al. 2023 and the paper's ID in your .bib file is 'LastName2023-xy'.

````
We can reference this paper in-text by adding [@LastName2023-xy] to the end of a sentence. This will produce a reference such as the one below for Tripp et al. 2017.
````
